### 2018-04-15 tex/paper.tex
Corrections to introduction

In doing this we are required to refine the model of contracts in a number of ways in order to fit with a radically different context. Taking the following example of an ``escrow'' contract we can explain the differences more concretely. The aim of this contract, written in functional pseudocode in the style of~\cite{PeytonJones:2000} involves players 1, 2 and 3. Player 1 is to pay an amount of money to player 2 on receipt of goods. She pays the sum into escrow controlled by player 3. There are two options for the money: if two players agree to \haskellinline{pay} it goes ahead; if, on the other hand, two of the players opt to \haskellinline{refund} the money, that is done. The \haskellinline{When} construct ensures fires when its first argument -- a condition -- becomes true; the second argument, a \haskellinline{Contract} itself, is then performed, and this makes the payment according to the players' \haskellinline{Choice}.

@@

In the traditional model, enforcement of the contract is the responsibility of the legal system. If player 1 doesn't pay the money into escrow, or play 3 chooses to keep it for herself, then we can assume that they can be sued for the money and probably damages on top, thus providing both legal and financial incentives for compliance. On the other hand, in the decentralised blockchain model, where there is no central authority, the contract needs to be enforced by design.

>>>>

In doing this we are required to refine the model of contracts in a number of ways in order to fit with a radically different context. Let us the following example of an ``escrow'' contract we can explain the motivation more concretely. The aim of this contract, written in functional pseudocode in the style of~\cite{PeytonJones:2000} involves three participants \haskellinline{1}, \haskellinline{2} and \haskellinline{3}. Participant \haskellinline{1} is to pay an amount of money to participant \haskellinline{2} on receipt of goods from her. Participant \haskellinline{1} pays the money into escrow controlled by participant \haskellinline{3}. There are two options for the money: if two participants agree to \haskellinline{pay} it to \haskellinline{2}, that goes ahead; if, on the other hand, two of the players opt to \haskellinline{refund} the money to \haskellinline{1}, that is done instead. The \haskellinline{When} construct ensures fires when its first argument -- a condition -- becomes true; the second argument, a \haskellinline{Contract} itself, is then performed, and this makes the payment according to the players' \haskellinline{Choice}.

@@

In the traditional model, enforcement of the contract is the responsibility of the legal system. If participant \haskellinline{1} doesn't pay the money into escrow, or participant \haskellinline{3} chooses to keep it for herself, then we can assume that they can be sued for the money and probably damages on top, thus providing both legal and financial incentives for compliance. On the other hand, in the decentralised blockchain model, where there is no central authority, the contract needs to be enforced by design.
